The Changing Shape of Empire: A GM Study of Chimú Bottles in Museum Collections

### 2022-11-02 supp/01-linear.Rmd
<init ms>

# render figure
sitefigure<-ggarrange(odgroup, bdgroup, ndgroup, blgroup, hgroup, rtgroup,
                  labels = c("a","b","c","d","e","f"),
                  ncol = 3, nrow = 2)
sitefigure
```

>>>>

# render figure
sitefigure<-ggarrange(odgroup, bdgroup, ndgroup, blgroup, hgroup, rtgroup,
                  labels = c("b","c","d","e","f","g"),
                  ncol = 3, nrow = 2)
sitefigure
```
